Directionality in Kilo-ton Scale Scintillating Neutrino Detectors

### 2013-07-16 Direction.tex
Halfway done with first references. --Lindley

\section{Introduction}
Liquid scintillator based detectors are responsible for several of the critical measurements that have cemented our understanding of three-neutrino oscillations. These measurements include KamLAND's measurement reactor antineutrino oscillation at a distance of $\sim$200~km, Borexino's measurement of $^{7}$Be solar neutrino oscillation and most recently the short baseline reactor antineutrino experiments that measured oscillations due to $\theta_{13}$ at a distance of 1~km: Daya Bay, Double Chooz, and RENO.  Scintillating neutrino detectors will continue to be important  for the next set of neutrino measurements from the determination of the neutrino mass hierarchy to elastic scattering measurements and sterile neutrino searches and for non-proliferation applications. Their scalability to large volumes makes them particularly attractive for neutrinoless double-beta ($0\nu\beta\beta$) decay searches, and currently one of the best limits for the $0\nu\beta\beta$ half-life comes from KamLAND-Zen.

>>>>

\section{Introduction}
Liquid scintillator based detectors are responsible for several of the critical measurements that have cemented our understanding of three-neutrino oscillations. These measurements include KamLAND's measurement reactor antineutrino oscillation at a distance of $\sim$200~km\cite{kam2013}, Borexino's measurement of $^{7}$Be solar neutrino oscillation\cite{borexino} and most recently the short baseline reactor antineutrino experiments that measured oscillations due to $\theta_{13}$ at a distance of 1~km: Daya Bay\cite{dbtwo}, Double Chooz\cite{dctwo, dchydrogen}, and RENO\cite{reno}.  Scintillating neutrino detectors will continue to be important  for the next set of neutrino measurements from the determination of the neutrino mass hierarchy to elastic scattering measurements and sterile neutrino searches and for non-proliferation applications. Their scalability to large volumes makes them particularly attractive for neutrinoless double-beta ($0\nu\beta\beta$) decay searches, and currently one of the best limits for the $0\nu\beta\beta$ half-life comes from KamLAND-Zen.
